### 2018-11-06 Sections/collision_handling_and_classical_errors.tex
Corrected some compile errors

Alternately, Alice might be a part of a distributed computation, where she didn't prepare the data in the first place. In this instance, the no-cloning theorem\index{No-cloning theorem}\footnote{The no-cloning theorem states that it is impossible to take a completely unknown quantum state and prepare an identical copy of it. That is, there is no quantum process\index{Quantum processes} implementing the map \mbox{$\mathcal{E}(\hat\rho\otimes\ket{0}\bra{0}) \to \hat\rho\otimes\hat\rho$} for unknown $\hat\rho$. Note that this result applies when $\hat\rho$ is arbitrary and unknown, but in general needn't apply if restricted to a particular basis, subject to other constraints, or we have \textit{a priori} knowledge of the state. \textit{Proof}:\index{No-cloning theorem!Proof} To see this, consider the evolution \mbox{$\hat{U}\ket\psi\ket{e} = e^{i\alpha(\psi,e)}\ket\psi\ket\psi$}, for some normalised ancillary state $\ket{e}$, where $\alpha$ denotes an irrelevant global phase factor. We have \mbox{$\langle\psi|\phi\rangle\langle e|e\rangle = \bra\psi\bra{e}\hat{U}^\dag\hat{U}\ket{\phi}\ket{e} = e^{-i[\alpha(\psi,e)-\alpha(\phi,e)]} \langle\psi|\phi\rangle^2$}. Since $\ket{e}$ is normalised, this implies \mbox{$|\langle\psi|\phi\rangle| = |\langle\psi|\phi\rangle|^2$}, which can only be true if \mbox{$ |\langle\psi|\phi\rangle|=0$} or \mbox{$ |\langle\psi|\phi\rangle|=1$}, which does not hold in general for arbitrary states $\ket\psi$ and $\ket\phi$. However, clearly if $\ket\psi$ and $\ket\phi$ are restricted to being equal or orthogonal then this constraint can be satisfied with an appropriate choice of $\hat{U}$.} implies that she cannot, in general, learn what the quantum state was, and therefore would be unable to make a second transmission attempt.

>>>>

Alternately, Alice might be a part of a distributed computation, where she didn't prepare the data in the first place. In this instance, the no-cloning theorem\index{No-cloning theorem}\footnote{The no-cloning theorem states that it is impossible to take a completely unknown quantum state and prepare an identical copy of it. That is, there is no quantum process\index{Quantum processes} implementing the map \mbox{$\mathcal{E}(\hat\rho\otimes\ket{0}\bra{0}) \to \hat\rho\otimes\hat\rho$} for unknown $\hat\rho$. Note that this result applies when $\hat\rho$ is arbitrary and unknown, but in general needn't apply if restricted to a particular basis, subject to other constraints, or we have \textit{a priori} knowledge of the state. \textit{Proof}:\index{No-cloning theorem!Proof} To see this, consider the evolution \mbox{$\hat{U}\ket\psi\ket{e} = e^{i\alpha(\psi,e)}\ket\psi\ket\psi$}, for some normalised ancillary state $\ket{e}$, where $\alpha$ denotes an irrelevant global phase factor. We have \mbox{$\langle\psi|\phi\rangle\langle e|e\rangle = \bra\psi\bra{e}\hat{U}^\dag\hat{U}\ket{\phi}\ket{e} = e^{-i[\alpha(\psi,e)-\alpha(\phi,e)]} \langle\psi|\phi\rangle^2$}. Since $\ket{e}$ is normalised, this implies \mbox{$|\langle\psi|\phi\rangle| = |\langle\psi|\phi\rangle|^2$}, which can only be true if \mbox{$ |\langle\psi|\phi\rangle|=0$} or \mbox{$ |\langle\psi|\phi\rangle|=1$}, which does not hold in general for arbitrary states $\ket\psi$ and $\ket\phi$. However, clearly if $\ket\psi$ and $\ket\phi$ are restricted to being equal or orthogonal then this constraint can be satisfied with an appropriate choice of $\hat{U}$, since this corresponds to classical cloning\index{Classical cloning}.} implies that she cannot, in general, learn what the quantum state was, and therefore would be unable to make a second transmission attempt.

### 2018-11-06 Sections/quantum_algorithms.tex
Corrected some compile errors

\subsection{Quantum advantage with shallow circuits}\index{shallow_circuits}

@@

It is incredibly difficult to compare quantum VS classical polynomial time computation, and 
currently we have noisy gates. Given $n$ qubits, depth $d$, and an error rate $\epsilon$, intuitively, we need the condition
\begin{align}
nd \ll 1/\epsilon
\end{align}
\noindent to hold, in order for a quantum algorithm to run successfully. If $d$ is large, then noise dominates and our circuit is classically simulable; on the other hand, if we have a large $n$ and small $d$ (constant depth circuits), we may observe a quantum speed up in the near future. Given these factors, we are motivated to examine shallow circuits. 
Now we will see that there is a distinction between constant depth circuits run using classical VS quantum algorithm.

The result is for the following hidden linear function (HLF) problem \cite{bravyi2018quantum}. Given an 
$n\times n$ symmetric binary matrix $A$, we specify a quadratic form
\begin{align}
q(x) = \vec x^T A \vec x \text{(mod 4)}.
\end{align}
\noindent The goal is to find a binary vector $\vec z \in {0,1}^n$ such that
% 
\begin{align}
q(x) = 2 \vec z^T \vec x
\end{align}
\noindent for all $\vec x$ in the binary null-space of A.

@@

\begin{figure}[h]
\includegraphics[trim = 0cm 0cm 0cm 0cm, clip, width=1.0\linewidth]{2DHLFcircuit.pdf}
\caption{\label{fig:2DHLF} Quantum circuit to solve the 2D HLF problem. }
\end{figure}

If we lay out the circuit in 2D (hence the 2D HLF problem), it only requires classically controlled Clifford gates between nearest neighbor qubits on a 2D grid. For an example, see Fig.~\ref{fig:2DHLFgrid}.
\begin{figure}[h]
\includegraphics[trim = 0cm 0cm 0cm 0cm, clip, width=0.8\linewidth]{2DHLF_grid.jpg}
\caption{\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid.}
\end{figure}

Now, comparing the quantum algorithm to a classical one, it has been proven that any probabilistic classical circuit with bounded input that solves the 2D HLF problem with high probability $\epsilon \leq 1/8$ must have depth increasing logarithmically with input size \cite{bravyi2018quantum}. The speed-up here is provided by quantum non-locality. 
% 
The fact that a problem can be solved with constant depth quantum circuits, but not classical ones shows that there is a clear separation in computational speed between the two cases.

>>>>

%
% Quantum advantage with shallow circuits}
%

\subsection{Quantum advantage with shallow circuits}\index{Shallow circuits}

@@

It is incredibly difficult to compare quantum VS classical polynomial time computation, and 
currently we have noisy gates. Given $n$ qubits, depth $d$, and an error rate $\epsilon$, intuitively, we need the condition
\begin{align}
nd \ll \frac{1}{\epsilon}
\end{align}
\noindent to hold, in order for a quantum algorithm to run successfully. If $d$ is large, then noise dominates and our circuit is classically simulable; on the other hand, if we have a large $n$ and small $d$ (constant depth circuits), we may observe a quantum speed up in the near future. Given these factors, we are motivated to examine shallow circuits. 
Now we will see that there is a distinction between constant depth circuits run using classical VS quantum algorithm.

The result is for the following hidden linear function (HLF) problem \cite{bravyi2018quantum}. Given an 
$n\times n$ symmetric binary matrix $A$, we specify a quadratic form
\begin{align}
q(x) = \vec x^T A \vec x \text{(mod 4)}.
\end{align}
\noindent The goal is to find a binary vector $\vec z \in {0,1}^n$ such that
\begin{align}
q(x) = 2 \vec z^T \vec x
\end{align}
\noindent for all $\vec x$ in the binary null-space of A.

@@

\begin{figure}[!htbp]
%\includegraphics[trim = 0cm 0cm 0cm 0cm, clip, width=1.0\linewidth]{2DHLFcircuit}
\caption{\comment{Insert figure}\label{fig:2DHLF} Quantum circuit to solve the 2D HLF problem. }
\end{figure}

If we lay out the circuit in 2D (hence the 2D HLF problem), it only requires classically controlled Clifford gates between nearest neighbor qubits on a 2D grid. For an example, see Fig.~\ref{fig:2DHLFgrid}.
\begin{figure}[!htbp]
\includegraphics[trim = 0cm 0cm 0cm 0cm, clip, width=0.8\linewidth]{2DHLF_grid}
\caption{\comment{Vector version please}\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid.}
\end{figure}

Now, comparing the quantum algorithm to a classical one, it has been proven that any probabilistic classical circuit with bounded input that solves the 2D HLF problem with high probability $\epsilon \leq 1/8$ must have depth increasing logarithmically with input size \cite{bravyi2018quantum}. The speed-up here is provided by quantum non-locality.

The fact that a problem can be solved with constant depth quantum circuits, but not classical ones shows that there is a clear separation in computational speed between the two cases.
